The Implications of Local Fluctuations in the Galactic Midplane for Dynamical Analysis in the \textit{Gaia} Era

### 2019-07-23 paper/ms.tex
Add paragraph on single measurement point

>>>>

\textbf{We would like to emphasize that in reality one only ever measures the
position and velocity of a star at a single instance in time, and not over any
significant portion of its orbit. However, if more than one star on the same
orbit can be identified, then it might be possible to constrain the disk
potential in analogy to how stellar streams are used to constrain the Galactic
potential \citep[e.g.][]{1999ApJ...512L.109J, 2001ApJ...551..294I,
2004ApJ...610L..97H, 2015ApJ...801...98S, 2015ApJ...803...80K,
2019MNRAS.483.1427L}. However, identifying the remnants of a disrupted open
cluster (the inner disk equivalent of a halo stellar stream) is a difficult
challenge. One would want to use the same constants of motion that we discuss
are suscept to significant errors. On the other hand, one could use chemical
tagging to identify a disrupted open cluster \citep{2002ARA&A..40..487F}, but
it may be difficult due to the large number of stars that are chemically
indistinguishable but are presumably born in different clusters
\citep{2018ApJ...853..198N}. An alternative technique that would deliver some
of the benefits of finding a disk stream may lie in measuring the
accelerations of stars \citep{2018arXiv181207581S}.}
